---
title: "project_3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## API Calls 

```{r} 
library(httr)
library(jsonlite)
k <- 5000
data <- list(rep(NA,k))
for(i in 0:k){
  j <- i*20
  get_url <- paste0("https://api.nytimes.com/svc/movies/v2/reviews/search.json?opening-date=2019-03-15:2021-03-15&api-key=wgJfZeGJBfKXqHXLC7MKYIhusdKGy2y5&offset=",j)
  nyt_data <- GET(get_url)
  nyt_data <- content(nyt_data)
  if(nyt_data[[3]] == FALSE){
    break
  }
  for(n in 1:length(nyt_data)){
    data[n+j] <- nyt_data[n]
  }
  Sys.sleep(10)
}
nyt_data$status_code
dim(data)
write_json(data, "nyt_movie_reviews_covid.json")
data <- read.csv("nyt_reviews_covid.csv")
```

```{r}
library(quanteda)
library(qdap)
library(stringr)
library(knitr)
library(tm)
summary <- data$summary 
summary_cleaned <- c()
for (i in seq_along(summary)){
    without_stopwords <- rm_stopwords(
    summary[i],
    stopwords = qdapDictionaries::OnixTxtRetToolkitSWL1, 
    unlist = FALSE,
    separate = TRUE,
    strip = TRUE,
    unique = FALSE,
    char.keep = NULL,
    lower.case = TRUE,
    names = FALSE,
    ignore.case = TRUE,
    apostrophe.remove = FALSE
  )
  text <- unlist(without_stopwords)
  text <- str_replace_all(text, pattern = '\n', replacement = "") # Remove \n
  text <- str_replace_all(text, pattern = '\u0092', replacement = "'") #Replace with quote
  text <- str_replace_all(text, pattern = '\u0091', replacement = "'") #Replace with quote
  text <- str_replace_all(text, pattern = '[:punct:]', replacement = "") #Remove punctuation
  text <- str_replace_all(text, pattern = '$', replacement = "") #Remove punctuation
  text <- str_replace_all(text, pattern = '-', replacement = "") #Remove punctuation
  text <- str_replace_all(text, pattern = '·', replacement = "") #Remove punctuation
  text <- str_replace_all(text, pattern="([8+[0-9]{4}+])", replacement="") # removing all 8000-8999 ASCII errors 
  text <- str_replace_all(text, pattern = 'M&#233;',replacement = "M") # fix broken M 
  text <- stemDocument(text, language = "english") # stemming words! 
  without_stopwords <- as.list(text)
  combine <- paste0(without_stopwords, collapse = " ")
  summary_cleaned <- append(summary_cleaned, combine) 
}
s_cleaned <- quanteda::dfm(summary_cleaned, verbose = FALSE)
dim(s_cleaned)
target_freq <- as.numeric(s_cleaned)
freqs_mat <- as.matrix(s_cleaned)
doc_freq <- apply(freqs_mat,2,function(x) mean(x>0))
idf <- 1/doc_freq
idf_mat <- rep(idf,nrow(freqs_mat), byrow = TRUE, nrow = nrow(freqs_mat))
tf_idf <- freqs_mat * idf_mat
```

```{r}
# get the top k tokens with the highest tf-idf value
k <- 15
i <- 1
keyword_lists <- data.frame(matrix(NA, nrow = nrow(tf_idf), ncol = k))
for (i in 1:nrow(tf_idf)){
  keyword_lists[i,] <- names(tf_idf[i,][order(tf_idf[i,],decreasing = TRUE)[1:k]])
}
head(keyword_lists)
```

```{r}
# TF-IDF and cosine similarity
# document clustering! with https://cran.r-project.org/web/packages/textmineR/vignettes/b_document_clustering.html
# changing cosine similarity to a distance 
csim <- tf_idf / sqrt(rowSums(tf_idf * tf_idf))
csim <- csim %*% t(csim)
cdist <- as.dist(1 - csim)
#h clust 
k <- 36
hc <- hclust(cdist, "ward.D2")
plot(hc)
clustering <- cutree(hc, h=2.5)
plot(hc, main = "'Complete' Hierarchical Clustering of Movie Review Summaries TF-IDF",
     xlab = "Cosine Similarity as Distance")
rect.hclust(hc, k, border = "#e56b6f")
p_words <- colSums(freqs_mat) / sum(freqs_mat)
cluster_words <- lapply(unique(clustering), function(x){
  rows <- freqs_mat[clustering == x,]
  # for memory's sake, drop all words that don't appear in the cluster
  rows <- rows[ , colSums(rows) > 0 ]
  colSums(rows) / sum(rows) - p_words[ colnames(rows) ]
})
```

```{r visualization}
library(formattable)
cluster_summary <- data.frame(cluster = unique(clustering),
                              size = as.numeric(table(clustering)),
                              top_words = sapply(cluster_words, function(d){
                                paste(
                                  names(d)[ order(d, decreasing = TRUE) ][ 1:5 ], 
                                  collapse = ", ")
                              }),
                              stringsAsFactors = FALSE)
formattable(cluster_summary)
# troubleshooting 
#which(grepl("and", data$summary))
```


```{r}
 library(data.table)
ratings <- read.csv("~/Downloads/title.ratings.tsv", sep = "\t")
require(data.table)
basics <- fread("~/Downloads/title.basics.tsv", sep = "\t")
merged <- merge(ratings, basics, by="tconst")
merged <- merged[which(merged$startYear >= 2019),] 
merged <- merged[which(merged$startYear <= 2021),] 
merged <- merged[which(merged$titleType == 'movie' | merged$titleType == 'tvmovie'),] 
write.csv(merged, "imdb_data.csv")
merged <- fread("~/Downloads/imdb_data.csv")
dim(merged)
#16557 rows lol 
final_merge <- merge(merged, data, by.x="primaryTitle", by.y="title")
# data cleaning, corre
opening_dates <- rep(NA, length(rownames(final_merge)))
for(i in seq_along(rownames(final_merge))){
  opening_dates[i] <- strftime(strsplit(as.character(final_merge$opening_date[i]),split="T")[[1]][1], format='%Y-%m-%d')
} 
final_merge$opening_date <- as.Date(unlist(opening_dates))
final_merge <- final_merge[!which(final_merge$opening_date <= 2019-03-15),] 




write.csv(final_merge, "nyt_and_imdb_data.csv")
mean(which(final_merge$averageRating > quantile(final_merge$averageRating,prob=1-21.85/100, na.rm = TRUE))
     %in% which(final_merge$critics_pick == 1))
```

Interesting stats for the project pre-covid analysis: 
- 21.85% of movies in this time period are "critics picks" 
- the average movie rating is a 6.37
- the top 3rd quartile is 7.1 movie rating 
- only .3536 in the top quartile of IMDB ratings also have a critics pick 
- at the same time, there is a significant correlation between the averageRating and the critics_pick 


```{r dates}
range(final_merge$opening_date) 
# making pre and post covid variable 
for(i in 1:length(rownames(final_merge))){
  if (final_merge$opening_date[i] >= "2020-03-15"){
    final_merge$covid[i] <- 1
  }
  else final_merge$covid[i] <- 0 
}
```

```{r}
library(data.table)
final_merge <- fread("~/Desktop/Data Mining/Data/nyt_and_imdb_data.csv")
final_merge$runtimeMinutes <- as.numeric(final_merge$runtimeMinutes)
hist(final_merge$opening_date, "days", format = "%b %y", 
     main="Histogram of Opening Dates of Movies vs. Density", 
     xlab="Movie Opening Date") # super interesting! 
hist(final_merge$opening_date, "months") # super interesting! 
# playing with different models 
ols <- glm(critics_pick ~ opening_date, data=final_merge, family="binomial")
summary(ols)
# high p value 
ols <- lm(averageRating ~ opening_date, data=final_merge)
summary(ols)
# high p value 
hist(final_merge$numVotes)
hist(final_merge$runtimeMinutes)
ols <- glm(critics_pick ~ runtimeMinutes + averageRating + numVotes, data=final_merge, family="binomial")
summary(ols)
# critics pick and average rating have a significant relatinship!! 
ols <- lm(averageRating ~ runtimeMinutes + numVotes + sent_sd + sent_sum, data=final_merge)
summary(ols)
# runtime, numVotes, critics pick, runtime, and sent sd have a significant relationship 
plot(final_merge$sent_sd, final_merge$averageRating) 
hist(final_merge$sent_sum)
cor(final_merge$averageRating, final_merge$numVotes)
```
```{r sentiment}
library(syuzhet)
for(i in 1:length(rownames(final_merge))){
  text <- get_tokens(final_merge$summary[i])
  syuzhet_vector <- get_sentiment(text, method="syuzhet")
  final_merge$sent_mean[i] <- mean(syuzhet_vector)
  final_merge$sent_sd[i] <- sd(syuzhet_vector)
  final_merge$sent_sum[i] <- sum(syuzhet_vector)
}
tail(final_merge)
# one data issue is that there are 267 summaries that do not have any positive or negative words in the dataset and therefore have a mean, sd, and sum of 0 
final_merge[which(final_merge$sent_sum ==max(final_merge$sent_sum)),] # most positive 
final_merge[which(final_merge$sent_sum ==min(final_merge$sent_sum)),] # most negative 
```


```{r}
library(caret)
library(Matrix)
library(glmnet)
library(MLmetrics)
# Exclude non-numeric
final_merge <- as.data.frame(final_merge)
wanted_cols <- c("averageRating", "runtimeMinutes", "covid", "numVotes", "critics_pick", "sent_mean", "sent_sd", "sent_sum")
final_merge$runtimeMinutes <- as.numeric(final_merge$runtimeMinutes)
reg_data <- final_merge[,wanted_cols]
reg_data[is.na(reg_data)] <- 0
# Defining the MSE
mse <-function(actual, pred){
  return(mean((actual - pred)^2))
}

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(reg_data$covid, k = 10)
#ols <- glm(covid ~ runtimeMinutes + averageRating + numVotes + critics_pick + sent_mean + sent_sd + sent_sum, data=final_merge, family="binomial")
#summary(ols)
#plot(ols)
# OLS
ols <-function(test, train){
  fit <- glm(train$covid ~ ., family="binomial", data=train)
  pred <- predict(fit, test)
  return(LogLoss(y_true = test$covid, y_pred = pred))
}

# STEPWISE
stepwise <-function(test, train){
  fit = glm(train$covid ~ ., family="binomial", data=train)
  fit_summary = summary(fit)$coefficients
  okay_features = rownames(fit_summary)[fit_summary[, 4] < 0.05]
  init_formula = paste('train$covid ~', paste(okay_features[-1], collapse ='+'))
  init_mod = glm(init_formula, data=train, family="binomial")
  step_mod <- step(init_mod, "~.", trace = 0)
  pred <- predict(step_mod, test)
  return(LogLoss(y_true = test$covid, y_pred = pred))
}

# LASSO 
lasso <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "covid")]), sparse = TRUE)
  y_train <- train$covid
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "covid")]), sparse = TRUE)
  y_test <- test$covid
  lasso_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
  lasso_mod <- glmnet(x_train, y_train, alpha = 1, family="binomial", lambda = lasso_cv$lambda.min)
  pred <- predict(lasso_mod, x_test)
  return(LogLoss(y_true = y_test, y_pred=pred))
}

# RIDGE
ridge <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "covid")]), sparse = TRUE)
  y_train <- train$covid
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "covid")]), sparse = TRUE)
  y_test <- test$covid
  ridge_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
  ridge_mod <- glmnet(x_train, y_train, alpha = 0, family="binomial", lambda = ridge_cv$lambda.min)
  pred <- predict(ridge_mod, x_test)
  return(LogLoss(y_true = y_test, y_pred=pred))
}

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- reg_data[test_folds[[i]], ]
  train <- reg_data[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)
# lasso performs the best almost all the time, so let's use lasso! 
```


```{r}
# using lasso! 
#lasso <-function(test, train){
#  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "covid")]), sparse = TRUE)
#  y_train <- train$covid
#  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "covid")]), sparse = TRUE)
#  y_test <- test$covid
#  lasso_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
#  lasso_mod <- glmnet(x_train, y_train, alpha = 1, family="binomial", lambda = lasso_cv$lambda.min)
#  pred <- predict(lasso_mod, x_test)
#  return(summary(lasso_cv))
#}
all_x <- Matrix(as.matrix(reg_data[ , -which(colnames(reg_data) == "covid")]), sparse = TRUE)
all_y <- reg_data$covid
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(reg_data[ , -which(colnames(reg_data) == "covid")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#for(i in 1:10){
#  test <- reg_data[test_folds[[i]], ]
#  train <- reg_data[-test_folds[[i]], ]
#  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "covid")]), sparse = TRUE)
#  y_train <- train$covid
#  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "covid")]), sparse = TRUE)
#  y_test <- test$covid
#  lasso_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
#  lasso_mod <- glmnet(x_train, y_train, alpha = 1, family="binomial", lambda = lasso_cv$lambda.min)
#  pred <- predict(lasso_mod, x_test)
#  norm_coefficients <- as.matrix(lasso_mod$beta)
#}
# average rating has the highest association with the "covid" variable, 
top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)] 
```
averageRating, runtimeMinutes, and sent_mean are the columns that overlap in the top 5 for normalized and not normalized

this means that averageRating, runtimeMinutes, and sent_mean have the strongest associations with the covid variable. This means that they had the strongest nonzero coefficients. 



```{r}
library(genderdata)
for (i in 1:length(nyt_reviews$author)) {
  gender <- gender(nyt_reviews$first_name)$gender
  nyt_reviews$gender[i] <- gender
  i <- i + 1
}
```


```{r}
# binarize genre
# do ols based only on genre columns, and see which ones are most correlated with covid
# see which are most highly correlated with critic's pick (NYT)
# see which are most highly correlated with IMDB rating
# look at difference between which genres are best
# model is just rating vs [genres]

# see which genres are most highly correlated with covid
# model is covid vs [genres]
head(final_merge)
final_merge <- as.data.frame(final_merge)

genres <- c()
p <- 1
for (i in 1:length(final_merge$genres)) {
  movie_genres <- get_tokens(final_merge$genres[i],",")
  if (length(movie_genres) > 0) {
    for (j in 1:length(movie_genres)) {
      if (!movie_genres[j] %in% genres) {
        genres[p] <- movie_genres[j]
        p <- p + 1
      }
    }
  }
}
remove <- c("\\n")
genres <- genres[!genres %in% remove]
for (i in genres) {
  final_merge[,i] <- 0
}
head(final_merge)

for (i in 1:length(final_merge$genres)) {
  movie_genres <- get_tokens(final_merge$genres[i],",")
  if (length(movie_genres) > 0) {
    for (j in movie_genres) {
      if (j != "\\n"){
        final_merge[,j][i] <- 1
      }
    }
  }
}
head(final_merge)
write.csv(final_merge, "~/Desktop/Data Mining/Data/movies_with_genres_new_merge.csv")


```


```{r}
covid <- c("covid")
wanted_cols <- c(covid, genres)
wanted_cols
genre_data <- final_merge[,wanted_cols]
colnames(genre_data)[which(colnames(genre_data) =="sci-fi")] <- "sci.fi"
class(genre_data)

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data$covid, k = 10)

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data[test_folds[[i]], ]
  train <- genre_data[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  #mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)
```

```{r}
# THIS IS USING GENRE TO PREDICT COVID VARIABLE
all_x <- Matrix(as.matrix(genre_data[ , -which(colnames(genre_data) == "covid")]), sparse = TRUE)
all_y <- genre_data$covid
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data[ , -which(colnames(genre_data) == "covid")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)] 
# It seems as though people really enjoyed watching music, documentary, drama genre movies during the COVID pandemic. 
```

```{r}

final_merge <- read.csv("~/Desktop/movies_with_genres_new_merge.csv")
head(final_merge)
critics_pick <- c("critics_pick")
wanted_cols <- c(critics_pick, genres)
wanted_cols
colnames(final_merge)
colnames(final_merge)[which(colnames(final_merge) =="sci.fi")] <- "sci-fi"
genre_data_pre_covid <- final_merge[final_merge$covid == 0, wanted_cols]
# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data_pre_covid$critics_pick, k = 10)

# OLS
ols <-function(test, train){
  fit <- glm(critics_pick ~ ., family="binomial", data=train)
  pred <- predict(fit, test)
  return(mse(test$critics_pick, pred))
}

# STEPWISE
stepwise <-function(test, train){
  fit = glm(critics_pick ~ ., family="binomial", data=train)
  fit_summary = summary(fit)$coefficients
  okay_features = rownames(fit_summary)[fit_summary[, 4] < 0.05]
  init_formula = paste('critics_pick ~', paste(okay_features[-1], collapse ='+'))
  init_mod = glm(init_formula, family="binomial", data=train)
  step_mod <- step(init_mod, "~.", family="binomial", trace = 0)
  pred <- predict(step_mod, test)
  return(mse(test$critics_pick, pred))
}

# LASSO 
lasso <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "critics_pick")]), sparse = TRUE)
  y_train <- train$critics_pick
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "critics_pick")]), sparse = TRUE)
  y_test <- test$critics_pick
  lasso_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
  lasso_mod <- glmnet(x_train, y_train, alpha = 1, family="binomial", lambda = lasso_cv$lambda.min)
  pred <- predict(lasso_mod, x_test)
  return(mse(y_test, pred))
}

# RIDGE
ridge <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "critics_pick")]), sparse = TRUE)
  y_train <- train$critics_pick
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "critics_pick")]), sparse = TRUE)
  y_test <- test$critics_pick
  ridge_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, family="binomial", intercept = TRUE)
  ridge_mod <- glmnet(x_train, y_train, alpha = 0, family="binomial", lambda = ridge_cv$lambda.min)
  pred <- predict(ridge_mod, x_test)
  return(mse(y_test, pred))
}

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data_pre_covid[test_folds[[i]], ]
  train <- genre_data_pre_covid[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)
```

```{r}
# PRE-COVID BEST GENRES BASED ON NYTREVIEWS
all_x <- Matrix(as.matrix(genre_data_pre_covid[ , -which(colnames(genre_data_pre_covid) == "critics_pick")]), sparse = TRUE)
all_y <- genre_data_pre_covid$critics_pick
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1,  family="binomial",  nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1,  family="binomial", lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data_pre_covid[ , -which(colnames(genre_data_pre_covid) == "critics_pick")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1,  family="binomial", nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1,  family="binomial", lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
nyt_pre_covid <- top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)] 
# The top genres pre-covid seem to be comedy, thriller, fantasy, western, and music based on the NYT Movie Reviews. 
qplot(not_norm_coefficients, 
     main= "Histogram of Coefficients of Lasso for NYT Rating Pre-Covid", 
     xlab= "Lasso Coefficients",
     geom="histogram"
     ) +
  scale_x_continuous(limits = c(-1,1))
```

```{r}
# NYTREVIEWS BEST GENRES POST-COVID
final_merge <- read.csv("~/Desktop/Data Mining/Data/movies_with_genres.csv")
critics_pick <- c("critics_pick")
wanted_cols <- c(critics_pick, genres)
genres
colnames(final_merge)[which(colnames(final_merge) =="sci.fi")] <- "sci-fi"
genre_data_post_covid <- final_merge[final_merge$covid == 1, wanted_cols]

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data_post_covid$critics_pick, k = 10)

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data_post_covid[test_folds[[i]], ]
  train <- genre_data_post_covid[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  #mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)

# POST-COVID BEST GENRES BASED ON NYTREVIEWS
all_x <- Matrix(as.matrix(genre_data_post_covid[ , -which(colnames(genre_data_post_covid) == "critics_pick")]), sparse = TRUE)
all_y <- genre_data_post_covid$critics_pick
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1,  family="binomial", nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1,  family="binomial", lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data_post_covid[ , -which(colnames(genre_data_post_covid) == "critics_pick")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, family="binomial", alpha = 1, nfolds = 5, intercept = TRUE)
plot(lasso_cv)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, family="binomial", lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
nyt_post_covid <- top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)] 
# The top genres post-covid seem to be action, thriller, drama, horror, and crime based on the NYT Movie Reviews.
qplot(not_norm_coefficients, 
     main= "Histogram of Coefficients of Lasso for NYT Rating Post-Covid", 
     xlab= "Lasso Coefficients",
     geom="histogram"
     ) +
  scale_x_continuous(limits = c(-1,1))

sim <- cbind(as.numeric(coef(lasso_cv)), 
             replicate(9,as.numeric(coef(cv.glmnet(x, y, family="binomial")))))
plot(1:k, rowMeans(sim[-1,] != 0) + runif(k, -0.025, 0.025), 
     xlab="Coefficient Index", ylab="Frequency not zero (jittered)",
     main="Results of Repeated Cross-Validated Lasso Fits")


```


```{r}
# IMDB BEST GENRES PRE-COVID
averageRating <- c("averageRating")
wanted_cols <- c(averageRating, genres)
colnames(final_merge)[which(colnames(final_merge) =="sci.fi")] <- "sci-fi"

genre_data_pre_covid <- final_merge[final_merge$covid == 0, wanted_cols]
#genre_data_pre_covid <- genre_data_pre_covid[!is.na(genre_data_pre_covid$averageRating),]

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data_pre_covid$averageRating, k = 10)

# OLS
ols <-function(test, train){
  fit <- lm(train$averageRating ~ ., data=train)
  pred <- predict(fit, test)
  return(mse(test$averageRating, pred))
}

# STEPWISE
stepwise <-function(test, train){
  fit = lm(train$averageRating ~ ., data=train)
  fit_summary = summary(fit)$coefficients
  okay_features = rownames(fit_summary)[fit_summary[, 4] < 0.05]
  init_formula = paste('train$averageRating ~', paste(okay_features[-1], collapse ='+'))
  init_mod = lm(init_formula, data=train)
  step_mod <- step(init_mod, "~.",  trace = 0)
  pred <- predict(step_mod, test)
  return(mse(test$averageRating, pred))
}

# LASSO 
lasso <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "averageRating")]), sparse = TRUE)
  y_train <- train$averageRating
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "averageRating")]), sparse = TRUE)
  y_test <- test$averageRating
  lasso_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, intercept = TRUE)
  lasso_mod <- glmnet(x_train, y_train, alpha = 1, lambda = lasso_cv$lambda.min)
  pred <- predict(lasso_mod, x_test)
  return(mse(y_test, pred))
}

# RIDGE
ridge <-function(test, train){
  x_train <- Matrix(as.matrix(train[ , -which(colnames(train) == "averageRating")]), sparse = TRUE)
  y_train <- train$averageRating
  x_test <- Matrix(as.matrix(test[ , -which(colnames(test) == "averageRating")]), sparse = TRUE)
  y_test <- test$averageRating
  ridge_cv <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 5, intercept = TRUE)
  ridge_mod <- glmnet(x_train, y_train, alpha = 0, lambda = ridge_cv$lambda.min)
  pred <- predict(ridge_mod, x_test)
  return(mse(y_test, pred))
}

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data_pre_covid[test_folds[[i]], ]
  train <- genre_data_pre_covid[-test_folds[[i]], ]
  #mod[i, "ols"] <- ols(test, train)
  mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)
# Lasso does the best job

all_x <- Matrix(as.matrix(genre_data_pre_covid[ , -which(colnames(genre_data_pre_covid) == "averageRating")]), sparse = TRUE)
all_y <- genre_data_pre_covid$averageRating
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data_pre_covid[ , -which(colnames(genre_data_pre_covid) == "averageRating")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
imdb_pre_covid <- top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)]
# Based on IMDB data, the best rated genres pre-covid seem to be documentary, thriller, and war.
all_coeffs <-c(not_norm_coefficients, yes_norm_coefficients)
library(ggplot2)
qplot(not_norm_coefficients, 
     main= "Histogram of Coefficients of Lasso for IMDb Rating Pre-Covid", 
     xlab= "Lasso Coefficients",
     geom="histogram"
     ) +
  scale_x_continuous(limits = c(-1,1))
```

```{r}
# IMDB BEST GENRES POST-COVID
averageRating <- c("averageRating")
wanted_cols <- c(averageRating, genres)
colnames(final_merge)[which(colnames(final_merge) =="sci.fi")] <- "sci-fi"
genre_data_post_covid <- final_merge[final_merge$covid == 1, wanted_cols]
#genre_data_post_covid <- genre_data_post_covid[!is.na(genre_data_post_covid$averageRating),]

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data_post_covid$averageRating, k = 10)

mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data_post_covid[test_folds[[i]], ]
  train <- genre_data_post_covid[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)
# Stepwise does the best job

all_x <- Matrix(as.matrix(genre_data_post_covid[ , -which(colnames(genre_data_post_covid) == "averageRating")]), sparse = TRUE)
all_y <- genre_data_post_covid$averageRating
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data_post_covid[ , -which(colnames(genre_data_post_covid) == "averageRating")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
imdb_post_covid <- top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)]
# Based on IMDB data, the best rated genres post-covid seem to be documentary, horror, and western.
qplot(not_norm_coefficients, 
     main= "Histogram of Coefficients of Lasso for IMDb Rating Post-Covid", 
     xlab= "Lasso Coefficients",
     geom="histogram"
     ) +
  scale_x_continuous(limits = c(-1,1))
```


```{r}
# IGNORE THIS
critics_pick <- c("critics_pick")
wanted_cols <- c(critics_pick, genres)
genre_data <- final_merge[,wanted_cols]

# Creating 10-folds
set.seed(123)
test_folds <- createFolds(genre_data$critics_pick, k = 10)


mod <- data.frame(matrix(nrow = 5, ncol = 5))
colnames(mod) <- c("ols", "stepwise", "lasso", "ridge", "min")
for(i in 1:10){
  test <- genre_data[test_folds[[i]], ]
  train <- genre_data[-test_folds[[i]], ]
  mod[i, "ols"] <- ols(test, train)
  mod[i, "stepwise"] <- stepwise(test, train)
  mod[i, "lasso"] <- lasso(test, train)
  mod[i, "ridge"] <- ridge(test, train)
}
for(i in 1:10){
  mod[i, "min"] <- names(which.min(mod[i, ]))
}
print(mod)

all_x <- Matrix(as.matrix(genre_data[ , -which(colnames(genre_data) == "critics_pick")]), sparse = TRUE)
all_y <- genre_data$critics_pick
#without norm
lasso_cv <- cv.glmnet(all_x, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
not_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(not_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")
#with norm 
all_x_scaled <- scale(Matrix(as.matrix(genre_data[ , -which(colnames(reg_data) == "covid")])))
lasso_cv <- cv.glmnet(all_x_scaled, all_y, alpha = 1, nfolds = 5, intercept = TRUE)
lasso_mod <- glmnet(all_x_scaled, all_y, alpha = 1, lambda = lasso_cv$lambda.min)
yes_norm_coefficients <- as.matrix(lasso_mod$beta)
plot(yes_norm_coefficients, main = "Coefficients of Lasso", ylab = "Beta")

top_tokens_not_norm <- rownames(not_norm_coefficients)[order(abs(not_norm_coefficients), decreasing = TRUE)[1:5]]
top_tokens_norm <- rownames(yes_norm_coefficients)[order(abs(yes_norm_coefficients), decreasing = TRUE)[1:5]]
sum(top_tokens_norm %in% top_tokens_not_norm)
top_tokens_norm[which(top_tokens_norm %in% top_tokens_not_norm)] 
qplot(not_norm_coefficients, 
     main= "Histogram of Coefficients of Lasso for NYT Rating Post-Covid", 
     xlab= "Lasso Coefficients",
     geom="histogram"
     ) +
  scale_x_continuous(limits = c(-1,1))
```

```{r}

ols <- glm(covid ~ averageRating + critics_pick, family = "binomial", data=final_merge)
summary(ols)

library(formattable)
results <- data.frame(imdb_pre_covid, nyt_pre_covid, imdb_post_covid, nyt_post_covid)

results <- data.frame(imdb = c(imdb_pre_covid, imdb_post_covid), 
                              nyt = c(nyt_pre_covid, nyt_post_covid))
sort2.df <- with(results, results[order(imdb_pre_covid, imdb_post_covid, nyt_pre_covid) , ])
sort2.df$nyt_post_covid <- sort2.df$nyt_post_covid[c(1,3,4,2)]


formattable(sort2.df, caption = "Top Results for Lasso Models of Reviews for IMDB and NYT Against Before/After COVID-19 Pandemic", align= c("l", "l", "l", "l"), 
            #area(col = 1:4) ~ function(x) !unique(x), 
            #area(col = 1:4) ~ color_tile("#B1CBEB", "#3E7DCC")
            #list(area(col = c("nyt_pre_covid", "nyt_post_covid", "imdb_post_covid", "imdb_pre_covid"))
            #   ~ color_tile("white", "pink"))
            list("span", nyt_pre_covid	 = color_tile("#f492f0", "#f492f0"),
            imdb_post_covid	 = color_tile("#f492f0", "#f492f0"), 
            imdb_pre_covid = color_tile("#f492f0", "#f492f0"),
            nyt_post_covid = color_tile("#f492f0", "#f492f0"))
            )



```





